---
title: "RMarkdown Practice"
author: "Samantha Swan"
date: "2024-01-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Practice: ## denotes a title, more #s leads to smaller text, must be a space between last text and the # Title, must be space between title name and #, adding a # in front of code will make it not run

## Title
### Title
#### Title

Using links, [____] is what it titles it, add link after

## Links

[BIS 15L Webpage](https://jmledford3115.github.io/datascibiol/)

## Practice
1. Test out arithmatic capabilities
```{r}
1+8
300000000/8375
17*6/2
```

2. Experiment with titles and syntax, # number directly corresponds to size without regards to order

## HAPPY THURSDAY
#### Test
### Test 2

3. Copy paste
```{r}
#install.packages("tidyverse")
library("tidyverse")
```


```{r}
ggplot(mtcars, aes(x = factor(cyl))) +
    geom_bar()
```

```{r}
ggplot(mtcars, aes(x = factor(cyl))) +
    geom_bar()
```

4. Now `knit` the file to html using the knit button at the top of the page.  
5. Lastly, commit and push this file to your GitHub repository.  