---
title: "lab_4_warmup"
output: html_document
date: "2024-01-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Warm-up
1. In a new R Markdown document, load the tidyverse and a package called `palmerpenguins`.
```{r}
library("tidyverse")
library("palmerpenguins")
```

2. What are the dimensions of the dataset `penguins`?

Dimensions are 344 by 8
```{r}
dim(penguins)
```

3. What are the names of the variables in the `penguins` dataset?

The names are species, island, bill length, bill depth, flipper length, body mass, sex, year
```{r}
glimpse(penguins)
```
Method done in class -> variables are columns so do names(penguins)

4. How many individuals were sampled on each island in the `penguins` dataset?

165 females, 168 males, 11 NAs so 344 total individual's matching the 344 rows
```{r}
summary(penguins)
```
Class method
```{r}
table(penguins$island)
```
OR
```{r}
summary(penguins$island)
```


5. What is the mean body mass for all individuals in the `penguins` dataset?

4201.754 grams
```{r}
mean(penguins$body_mass_g, na.rm=T)
```

